### 2025-01-08 paper/icml25/first/sects/experiments.tex
hardware setup

\paragraph{Hardware Setup}
\texttt{\color{DarkOrchid}TODO: Qua metterei le specifiche CPU e GPU del vostro server}

>>>>

\paragraph{Hardware Setup}
Our experiments were conducted on a cluster of machines composed of 2 computational nodes, each with one Nvidia Tesla V100 GPU (with 32GB of memory), 200GB of RAM, and two Intel Xeon Gold 6226R processors (32 cores each).
